---
output:
  html_document: default
params:
  skill: 1
---
<style>
/* latin */
@font-face {
  font-family: 'Calibri';
  font-style: normal;
  font-weight: 400;
  src: local('Calibri'), url(https://fonts.gstatic.com/l/font?kit=J7afnpV-BGlaFfdAhLEY67FIEjg&skey=a1029226f80653a8&v=v10) format('woff2');
  unicode-range: U+0000-00FF, U+0131, U+0152-0153, U+02BB-02BC, U+02C6, U+02DA, U+02DC, U+2000-206F, U+2074, U+20AC, U+2122, U+2191, U+2193, U+2212, U+2215, U+FEFF, U+FFFD;
}
@page {
size: 100mm 150mm;
}
body {
border: black 1mm solid;
height: 151.5mm;
width: 101mm;
font-family: "Calibri";
}
.main-container {
display: flex;
flex-direction: column;
justify-content: space-between;
height: 150mm;
width: 100mm;
}
h1 {
margin-top:5mm;
margin-bottom: 3mm
}
hr{
margin-top: 3mm;
margin-bottom: 3mm;
}
</style>

```{r,include=FALSE}
library(tidyverse)
library(googlesheets)
library(waffle)
library(ggtern)
gs_auth(cache=T)
sheet <- gs_key("1pVDMAY6-BM22BIzeIHffbtRGcAF7e0lcXcuLlXMom0w")
card <- gs_read(sheet)[params$skill,]
```

<div>
# Possible components

```{r, results='asis', echo = F} 
card$components %>% 
  str_split(",") %>% 
  magrittr::extract2(1) %>% 
  str_trim() %>% 
  map_chr(~glue::glue("* {.}")) %>% 
  glue::glue_collapse("\n")
```
</div>

<div>
<hr>
</div>

<div>
# Resources

```{r, results='asis', echo = F} 
card$resources %>% 
  str_split(",") %>% 
  magrittr::extract2(1) %>% 
  str_trim() %>% 
  map_chr(~glue::glue("* {.}")) %>% 
  glue::glue_collapse("\n")
```
</div>
