---
output:
  html_document: default
params:
  skill: 1
---
<style>
/* latin */
@font-face {
  font-family: 'Calibri';
  font-style: normal;
  font-weight: 400;
  src: local('Calibri'), url(https://fonts.gstatic.com/l/font?kit=J7afnpV-BGlaFfdAhLEY67FIEjg&skey=a1029226f80653a8&v=v10) format('woff2');
  unicode-range: U+0000-00FF, U+0131, U+0152-0153, U+02BB-02BC, U+02C6, U+02DA, U+02DC, U+2000-206F, U+2074, U+20AC, U+2122, U+2191, U+2193, U+2212, U+2215, U+FEFF, U+FFFD;
}
@page {
size: 100mm 150mm;
}
body {
border: black 1mm solid;
height: 151.5mm;
width: 101mm;
font-family: "Calibri";
}
.main-container {
display: flex;
flex-direction: column;
justify-content: space-between;
height: 150mm;
width: 100mm;
}
h1 {
margin-top:5mm;
margin-bottom: 3mm
}
hr{
margin-top: 3mm;
margin-bottom: 3mm;
}
</style>

```{r,include=FALSE}
library(tidyverse)
library(googlesheets)
library(waffle)
library(ggtern)
gs_auth(cache=T)
sheet <- gs_key("1pVDMAY6-BM22BIzeIHffbtRGcAF7e0lcXcuLlXMom0w")
card <- gs_read(sheet)[params$skill,]
```

<div>
# `r card$skill`

`r card$description`
</div>
<div>
<hr>
</div>

<div>
```{r ternplot, echo=F, warning=F, message=F, fig.height=4, fig.width=4, out.extra='style="height: 55mm; object-fit: cover"'}
card %>% 
  mutate(
    total = tech+analytical+data_management, 
    tech = tech/total, 
    analytical = analytical/total, 
    data_management = data_management/total,
    total = ceiling(total/5)
) %>% 
    ggplot(aes(x=analytical, y = tech, z = data_management)) +
  geom_point(size = 5, show.legend = F) + 
  coord_tern() + 
  theme_linedraw() + 
  theme_hidegrid() + 
  theme_zoom_center(1.1) + 
  theme(
    axis.text = element_blank(), 
    axis.ticks = element_blank(), 
    tern.panel.expand = 0.4
    ) + 
  scale_size_area(limits = c(1,3)) + 
  labs(x = "Analytical", y = "Technical", z = "Data Mgmt")
```

```{r domainplot, echo=F,warning=F, message=F, out.extra='style="height: 18mm; object-fit: cover;"', fig.height=1, fig.width=4}
ggplot(card) +
  geom_waffle(
    aes(fill=factor(domain),values=domain), 
    n_rows=1, 
    colour = "white", 
    show.legend = F
    )  +
  theme_minimal() +
  coord_fixed() + 
  scale_y_continuous(breaks=1, labels = "Domain Knowledge") +
  scale_x_continuous(
    breaks=c(1,3,5), 
    labels = c("Low","Med","High"), 
    limits = c(.5,6), 
    position = "top", 
    expand = c(0.02,0)
    ) + 
  theme(
    panel.grid = element_blank(), 
    axis.text = element_text(colour="black")
  ) + 
  scale_fill_manual(values = rev(RColorBrewer::brewer.pal(5, "RdBu"))[card$domain])

```
</div>
